Kindly Bent to Free Us

### 2019-11-18 kindly/intro.tex
Add link to the prototype.

A large proportion of systems programming is focused on the proper
handling of resources, like file handles, network connections, or
dynamically allocated memory. Each of these resources comes with a
protocol that prescribes the correct use of its API.
For examples, a file handle appears as the result of opening a
file. If it was opened for reading, then read operations will succeed,
but write operations will fail. Once the handle is closed, it cannot
be used for reading or writing, anymore.

Dynamic allocation of memory is analogous. An API call returns a
pointer to a memory area, which can then be read and written to until
the memory is released by another API call.

@@

\begin{itemize}
\item A type system that encodes linearity and affinity with
  borrowing. The type system is polymorphic with respect to types as
  well as kinds that express constraints on the number of uses of a value.
\item An extension of the HM(X) framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, principal type inference.
\item Full account of the metatheory for type inference and type soundness.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\item An implementation of the type inference algorithm including all
  constraint simplification and extended with pattern matching. A
  web implementation of the typechecker is available, its URL is given in the
  non-anonymous supplementary material, and we plan to submit it for
  artifact evaluation.
\end{itemize}

>>>>

A large proportion of systems programming is focused on the proper
handling of resources, like file handles, network connections, or
dynamically allocated memory. Each of these resources comes with a
protocol that prescribes the correct use of its API.
For examples, a file handle appears as the result of opening a
file. If it was opened for reading, then read operations will succeed,
but write operations will fail. Once the handle is closed, it cannot
be used for reading or writing, anymore.
%
Dynamic allocation of memory is analogous. An API call returns a
pointer to a memory area, which can then be read and written to until
the memory is released by another API call.

@@

\begin{itemize}
\item A type system that encodes linearity and affinity with
  borrowing. The type system is polymorphic with respect to types as
  well as kinds that express constraints on the number of uses of a value.
\item An extension of the HM(X) framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, principal type inference.
\item Full account of the metatheory for type inference and type soundness.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\item A prototype implementation of the type inference algorithm, including all
  constraint simplification and extended with pattern matching,
  available at \url{https://affe.netlify.com/}.
\end{itemize}
